---
title: "Scrape SBACC"
author: "Rachdyan"
date: "2023-02-02"
output: github_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

We want to scrape the Professional Manager Certification (PMC) data from SBACC website here: https://sbacc.org.sg/services/pmc-search/

First, load the needed libraries for the project

```{r library, echo = T, message = F, warning = F}
library(rvest)
library(tidyr)
library(dplyr)
library(stringr)
library(knitr)
library(kableExtra)
```

## Get all the profile links

Get all the profile links from the directory

```{r scrape_link, cache = T}

link <- c()

## There are a total of 35 pages in the directory
for(i in 1 :35){
  url <- paste("https://sbacc.org.sg/services/pmc-search/page/", i, "/?wpbdp_view=search&dosrch=1&listingfields%5B11%5D&listingfields%5B1%5D", sep = "")
  page <- read_html(url)
  temp_link <- page %>% html_nodes("div[class='listing-title']") %>% html_nodes("a") %>% html_attr("href")
  link <- c(link, temp_link)
}

## See the link example
head(link)
```


## Scrape data from the profile link

Get all the profile links from the directory

```{r scrape_profile, cache = T}
profil_df <- data.frame()

for(i in 1:length(link)){
  url <- link[i]
  page <- read_html(url)
  name <- page %>% html_nodes("h1[class='page-header-title clr']") %>%  html_text2()
  
  pmc_code <- page %>%  html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-pmc_code wpbdp-field-meta wpbdp-field-type-textfield wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  position <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-position wpbdp-field-meta wpbdp-field-type-textfield wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  company <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-company wpbdp-field-meta wpbdp-field-type-textarea wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  office <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-office wpbdp-field-meta wpbdp-field-type-textfield wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  phone <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-phone_number wpbdp-field-meta wpbdp-field-type-textfield wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  verif <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-pmc_verification wpbdp-field-meta wpbdp-field-type-radio wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  status <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-certification_status wpbdp-field-meta wpbdp-field-type-radio wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  experties <- page %>% html_nodes("div[class='wpbdp-field-display wpbdp-field wpbdp-field-value field-display field-value wpbdp-field-area_of_expertise wpbdp-field-meta wpbdp-field-type-textarea wpbdp-field-association-meta  ']") %>% 
    html_nodes("div[class='value']") %>% html_text2() %>% ifelse(identical(., character(0)), NA, .)
  
  temp_df <- data.frame(name = name, pmc_code = pmc_code, position = position, 
                        company = company, office = office, phone = phone, 
                        verif = verif, status = status, experties = experties)
  profil_df <- rbind(profil_df, temp_df)
}


```

Display the data

```{r display_data, echo = T}

profil_df %>% kable() %>% kable_styling("striped") %>%
  scroll_box(height = "500px", width = "100%", fixed_thead = T)

```

## Export the data

Export the data as a csv file

```{r save_data, echo=TRUE}

write.csv(profil_df, "./data/PMC_data.csv", col.names = F)

```

